Figures

### 2018-03-13 scripts/analysis.Rmd
add some exploratory plots
plots on separate pages by adding captions

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5.5, fig.height = 4.2)
```

@@

```{r k_viz, echo=FALSE, message=FALSE}

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5.5, fig.height = 4.2, fig.pos = 'H')
```

@@

```{r k_viz, echo=FALSE, message=FALSE, fig.cap="Distribution of Vollenweider's k in low and high connectivity partitions at the IWS and NWS scales."}

@@

```{r graphical_exploratory_analysis, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8.4, fig.cap="Exploratory plots"}

```{r maps, echo=FALSE, fig.cap="Map of lakes with low distance to nearest upstream lake at the NWS scale."}

<!-- * Olin Lake has a completely undeveloped shoreline -->
<!-- * Madison Lake is impaired according to MPCA -->

```{r conceptual_summary, echo=FALSE, fig.cap="Connectivity metric effects on lake processing."}
dt <- data.frame(
  rbind(
        c("lakeconnection", "DR_Stream", "higher", "lower", "higher", "lake"), 
        c("upstream lake area", "lower", "higher", "lower", "higher", "lake"), 
        c("link_length", "lower", "higher", "lower", "higher", "stream"), 
        c("baseflow", "higher", "higher", "lower", "higher", "stream"), 
        c("stream order ratio", "higher", "higher", "lower", "higher", "stream"),
  c("upstream lake distance", "lower", "higher", "lower", "higher", "lake-stream"), 
        c("stream density", "higher", "higher", "lower", "higher", "stream")))

names(dt) <- c("metric", "direction", "k", "connectivity", "in_lake_processing", "axis")

knitr::kable(dt)
```
